---
title: "What is the relationship between sleep and productivity?"
author: "Wed13CC_ABS3100_Group06 in Canvas; 510477536"
subtitle: "Project 2"
date: "University of Sydney | DATA1001 | September 2020"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

<br>

# Executive Summary

<br>

# Full Report

## Initial Data Analysis (IDA)

```{r, eval=F}
install.packages("googlesheets4")
```

```{r}
library(googlesheets4)
library(tidyverse)
library('plotly')
```

```{r}
# Read in your survey data
survey = read_sheet("https://docs.google.com/spreadsheets/d/1akjF8jg0R76Q7Cxui5n_VhM9HpwU3naPa_gypXGqBRM/edit?usp=sharing")
<<<<<<< HEAD
=======
survey$age = ordered(survey$age, levels=c("15-17", "18-21", "22-25", "30 and above"))
survey$wake_up <- ordered(survey$wake_up, levels = c("5am or earlier", "6am", "7am", "8am", "9am", "10am", "11am", "12pm or later"))
survey$go_bed <- ordered(survey$go_bed, levels = c("Earlier than 9pm", "10-11pm", "11pm-12am", "12-1am", "1am-2am", "Later than 2am"))
survey$working_time <- ordered(survey$working_time, levels = c("0-2 hours", "2-4 hours", "4-6 hours", "6-8 hours", "8 or more hours"))
>>>>>>> a299a38 (asdf)
```

<br>

## Research Questions 
General

age
```{r}
<<<<<<< HEAD
survey$`How old are you?` = ordered(survey$`How old are you?`, levels=c("15-17", "18-21", "22-25", "30 and above"))
survey$`On average, what time do you usually go to bed each night?` = ordered(survey$`On average, what time do you usually go to bed each night?`, levels=c("Earlier than 9pm", "9-10pm", "10-11pm", "11pm-12am", "12-1am", "1am-2am", "Later than 2am"))  
wake_up = survey$`On average, what time do you wake up each morning?`
go_affect = survey$`Does going to bed early affect how productive you are the next day?`
wake_affect = survey$`Does waking up early affect how productive you are that day?`
survey$`How many hours on average do you sleep each night?` = as.character(survey$`How many hours on average do you sleep each night?`)
sleeping_hours = survey$`How many hours on average do you sleep each night?`
eightplus_affect = survey$`Does getting 8+ hours of sleep per night affect how productive you are?`
enough_sleep = survey$`Do you believe you get enough sleep?`
r_u = survey$`Do you consider yourself a productive person?`
u_believe = survey$`Do you believe sleep has an effect on your productivity`
=======
a = table(survey$age)
a
barplot(a, main="Age")
>>>>>>> a299a38 (asdf)
```

job
```{r}
pp <- plot_ly(survey, labels= ~job, type='pie', textposition = 'inside', textinfo = 'label+percent', showlegend= FALSE)
pp <- pp %>% layout(title = 'job')
pp
```

rising hour
```{r}
a = table(survey$wake_up)
a
barplot(a, main="Rising Hour")
```

bed time

```{r}
a = table(survey$go_bed)
a
barplot(a, main="Bed Time")
```

sleeping hours

```{r}
a = table(survey$sleeping_hours)
a
barplot(a, main="Sleeping Hours")
```

working time

```{r}
a = table(survey$working_time)
a
barplot(a, main="Working Time")
```


age vs average hour to sleep
job vs average hour to sleep
```{r}
# length of any variable is the number of people involved in the survey
<<<<<<< HEAD
survey$age = ordered(survey$age, levels=c("15-17", "18-21", "22-25", "30 and above"))
=======
>>>>>>> a299a38 (asdf)
n <- length(survey$age)
for (i in 1:n) {
  if (survey$sleeping_hours[i]=="3 or less") {
    survey$sleeping_hours[i] <- 3
  } else if (survey$sleeping_hours[i]=="10 or more") {
    survey$sleeping_hours[i] <- 10
  }
}
survey$sleeping_hours <- as.numeric(as.character(unlist(survey$sleeping_hours)))

table(survey$age, survey$sleeping_hours)

p1 = plot_ly(survey, x = ~sleeping_hours, color = ~age, type = 'box')
p1 <- p1 %>% layout(showlegend = FALSE)
p1 <- p1 %>% layout(title="age vs average hour to sleep")
p1

table(survey$job, survey$sleeping_hours)

p2 = plot_ly(survey, x = ~sleeping_hours, color = ~job, type = 'box')
p2 <- p2 %>% layout(showlegend = FALSE)
p2 <- p2 %>% layout(title="job vs average hour to sleep")
p2
```

Does going to bed early affect how productive you are the next day?
```{r}
<<<<<<< HEAD
p3 = plot_ly(survey, y =~`Does going to bed early affect how productive you are the next day?`, type="bar")
p3
=======
a = table(survey$`Does going to bed early affect how productive you are the next day?`)
barplot(a, main="Does going to bed early affect how productive you are the next day?", xlab="scores(1-10)", ylab="frequency")
```

Does waking up early affect how productive you are that day?
```{r}
a = table(survey$`Does waking up early affect how productive you are that day?`)
barplot(a, main="Does waking up early affect how productive you are that day?", xlab="scores(1-10)", ylab="frequency")
```

Do you believe sleep has an effect on your productivity?
```{r}
survey$`Do you believe sleep has an effect on your productivity` = ordered(survey$`Do you believe sleep has an effect on your productivity`, levels=c("Strongly Disagree", "Partly disagree", "Neither agree nor disagree", "Partly Agree", "Strongly Agree"))

table(survey$`Do you believe sleep has an effect on your productivity`)
p3 = plot_ly(survey, x = ~`Do you believe sleep has an effect on your productivity`, type='box')
p3 <- p3 %>% layout(title="Do you believe sleep has an effect on your productivity?")
p3
```

how much work 
vs sleeping hours
vs time wake-up (. vs wake up early effect?)
vs go bed (. vs sleep early effect?)

```{r}
survey$sleeping_hours <- as.character(survey$sleeping_hours)

for (i in 1:n) {
  if (survey$sleeping_hours[i]=="3") {
    survey$sleeping_hours[i] <- "< 3 hours"
  } else if (survey$sleeping_hours[i]=="4") {
    survey$sleeping_hours[i] <- "4 hours"
  } else if (survey$sleeping_hours[i]=="5") {
    survey$sleeping_hours[i] <- "5 hours"
  } else if (survey$sleeping_hours[i]=="6") {
    survey$sleeping_hours[i] <- "6 hours"
  } else if (survey$sleeping_hours[i]=="7") {
    survey$sleeping_hours[i] <- "7 hours"
  } else if (survey$sleeping_hours[i]=="8") {
    survey$sleeping_hours[i] <- "8 hours"
  } else if (survey$sleeping_hours[i]=="9") {
    survey$sleeping_hours[i] <- "9 hours"
  } else if (survey$sleeping_hours[i]=="10") {
    survey$sleeping_hours[i] <- "> 10 hours"
  }
}

survey$sleeping_hours <- ordered(survey$sleeping_hours, levels= c("< 3 hours", "4 hours", "5 hours", "6 hours", "7 hours", "8 hours", "9 hours", "> 10 hours"))

p4 = plot_ly(survey, x = ~working_time, y = ~sleeping_hours)
p4 <- p4 %>% layout(title="working_time vs sleeping_hours")
p4

# same but box plot, above 2D histogram
p6 = plot_ly(survey, x = ~working_time, color= ~sleeping_hours, type= 'box')
p6 <- p6 %>% layout(title="working_time vs sleeping hours?")
p6

# wake up
p4 = plot_ly(survey, x = ~working_time, color = ~wake_up, type = 'box')
p4 <- p4 %>% layout(title="working_time vs rising hour")
p4

p5 = plot_ly(survey, x = ~`Does waking up early affect how productive you are that day?`, color = ~wake_up, type = 'box')
p5 <- p5 %>% layout(title="Does going to bed early affect how productive you are the next day? vs rising hour")
p5

# go bed
p4 = plot_ly(survey, x = ~working_time, color = ~go_bed, type = 'box')
p4 <- p4 %>% layout(title="working_time vs bed time")
p4

p5 = plot_ly(survey, x = ~`Does going to bed early affect how productive you are the next day?`, color = ~go_bed, type = 'box')
p5 <- p5 %>% layout(title="Does going to bed early affect how productive you are the next day? vs bed time")
p5
```


Question 2 
What is the relationship between the amount of hours slept by an individual and their productivity?

Graph 2 
Do you think you get enough sleep vs how productive you think you are - the person’s perception of their own productivity

```{r}
p6 = plot_ly(survey, x = ~`Do you believe you get enough sleep?`, color= ~`Do you consider yourself a productive person?`, type= 'box')
p6 <- p6 %>% layout(title="Do you believe you get enough sleep? vs Do you consider yourself a productive person?")
p6
```

Graph 3
	"Do you believe sleep has an effect on your productivity" vs R u productive person? 
	
```{r}
p6 = plot_ly(survey, x = ~`Do you believe sleep has an effect on your productivity`, y= ~`Do you consider yourself a productive person?`)

p6 <- p6 %>% layout(title="Do you believe sleep has an effect on your productivity vs Do you consider yourself a productive person?")
p6
```
	
Graph 4
	8 + vs Pro
	
```{r}
p6 = plot_ly(survey, x = ~`Does getting 8+ hours of sleep per night affect how productive you are?`, color= ~`Do you consider yourself a productive person?`, type= 'box')
p6 <- p6 %>% layout(title="Does getting 8+ hours of sleep per night affect how productive you are? vs Do you consider yourself a productive person?")
p6
>>>>>>> a299a38 (asdf)
```

G1

Hours vs enough sleeping?

```{r}
p6 = plot_ly(survey, x = ~`Do you believe you get enough sleep?`, color= ~sleeping_hours, type= 'box')
p6 <- p6 %>% layout(title="Do you believe you get enough sleep? vs sleeping hours?")
p6
```

hours vs consider produc?

```{r}
p6 = plot_ly(survey, x = ~sleeping_hours, color= ~`Do you consider yourself a productive person?`, type= 'box')
p6 <- p6 %>% layout(title="working time vs Do you consider yourself a productive person?")
p6
```

Hours vs 8+

```{r}
p6 = plot_ly(survey, x = ~`Does getting 8+ hours of sleep per night affect how productive you are?`, color= ~sleeping_hours, type= 'box')
p6 <- p6 %>% layout(title="Does getting 8+ hours of sleep per night affect how productive you are? vs sleeping hours?")
p6
```

working vs sleeping time

```{r}
p6 = plot_ly(survey, x = ~working_time, color= ~sleeping_hours, type= 'box')
p6 <- p6 %>% layout(title="working_time vs sleeping hours?")
p6
```

Hours vs believe sleep affect u 

```{r}
p6 = plot_ly(survey, x = ~`Do you believe sleep has an effect on your productivity`, color= ~sleeping_hours, type= 'box')
p6 <- p6 %>% layout(title="Do you believe sleep has an effect on your productivity vs sleeping hours?")
p6
```



<br>

## Related Articles

<br>

## References
Use APA

<br>

## Acknowledgments
When did you team meet (date and time), and what did each team member contribute?
